%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Freelance Data Analyst} % Job title
    {Wyzant} % Organization
    {Online} % Location
    {Jul. 2019 - Onward} % Date(s)
    {Notable Client Projects}
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {\footnotesize Research and implementation of Full Factorial Orthogonal Design of Experiments for simultaneous inverse regression confidence intervals of multiple feature variances to the 3rd degree of differentiation.}
        \begin{itemize}
            \item {\scriptsize Inverse regression, generation of Design matrices,ANOVA regression, Bisection method optimizations, Multivariate delta symbolic regression, precision to at least 20 decimal places, Spectral Decomposition,chi-square statistic evaluations,T value confidence interval evaluation were required.}
        \end{itemize}
        \item {\footnotesize  Consultation and implementation of Predictive analysis of Spotify artists Monthly Listeners so as to identity a key metric or set of metrics that influence each each artists number of monthly listeners.}
        \begin{itemize}
            \item {\scriptsize Statistical techniques of Variance Inflation Factors, loss metric of root mean squared error, Jacque Bera statistic, PCA regression, collinearity analysis, and feature under sampling were used.}
        \end{itemize}
        \item {\footnotesize  Implement on the day Stock sentiment predictive analysis.}
        \begin{itemize}
            \item {\scriptsize Used yfinance api data to preprocess to 100 day shifted rolling percent change matrix}
            \item {\scriptsize Used state of the art extreme gradient boosting algorithm (XGBoost) for hyperparameter tuning.} 
            \item {\scriptsize Then moved on to Multivariate normal Tree Node analysis of node weighted relevancy}
            \item {\scriptsize interpret model weighted nodes to json via shap analysis}
        \end{itemize}
        
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Google Developers Student Club Lead, TKU/ Google Developers Student Club Core Member, NTNU} % Job title
    {\newline Google Developers} % Organization
    {Taipei,Taiwan} % Location
    {Apr. 2020 - Onwards} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Co Host study jams with local foreign developer meetups}
        \item {Invite guest speakers from Vice Presidents of major insurance companies, to local blockchain startups to your regular developer as a business owner and many more}
      \end{cvitems}
      %\begin{cvsubentries}
      %  \cvsubentry{}{KNOX(Solution for Enterprise Mobile Security) Penetration Testing}{Sep. 2013}{}
      %  \cvsubentry{}{Smart TV Penetration Testing}{Mar. 2011 - Oct. 2011}{}
      %\end{cvsubentries}
    }

%---------------------------------------------------------
  \cventry
    {AI Specialist Engineer} % Job title
    {Taiwan Tech Arena} % Organization
    {Taipei, Taiwan} % Location
    {May. 2020 - Oct. 2020} % Date(s)
    {
      {\footnotesize Main challenge to solve from beginning to end was the real time, two 3840x2160 pixels 180 degree fisheye camera construction of calibrated panoramic video views in real time on the edge device.\newline}
             {My tasks include:}
             \begin{itemize}
                \setlength\itemsep{0em}
                \item {\scriptsize OS level dependency configurations for cloud instances and NVIDA jetson Xavier device (gstreamer,fpga etc..)}  
                \item {\scriptsize Latest CUDA/Cudnn compilations for capadability with nvidia-docker2}
                \item {\scriptsize Opencv source code adaptation between arm64 tegra processors and x64-86 processors}
                \item {\scriptsize Opencv c++ stitching objects separation of estimateTransform, composePanaroma for stitching speed up}
                \item {\scriptsize Adaptation of opencv c++ 2.4 CUDA image blending object into opencv 4.5 C++ stitching object for composePanorama step to utilize edge device GPU}
                \item {\scriptsize Patch opencv c++ optimized source code to opencv-python API via .so file env symlinks}
                \item {\scriptsize Video to 2d real time image projection homographies of key feature points}
                \item {\scriptsize CV fisheye to panaroma callibrations}
                \item {\scriptsize Contribute to 6 main analysis feature of mainly "camera panning", "zooming","slow motion"}
                \item {\scriptsize Containerization of optimized source for cross platform operations}
                \item {\scriptsize Apache Airflow dags of barebone automated video delivery and running of analysis from edge device to cloud instance}
                \item {\scriptsize Patch feature descriptor and feature detection algorithms from opencv 4.3-dev version to 4.5 }
                \item {\scriptsize Generate CPack binary deb files for single opencv compilation automation}
                \item {\scriptsize administer AWS cloud IAM roles,VPC priviledges and set budget/usage alarms}
            \end{itemize}
    }
%---------------------------------------------------------
  \cventry
    {Analytics Engineer Intern} % Job title
    {\newline FiO.one} % Organization
    {Taipei, Taiwan} % Location
    {July. 2021 - Sept. 2021} % Date(s)
    {Manage and build bare bones prototype of end to end Recommendation System for highschool students to their Universities respective departments. Responsible for data collection, database architecting, Normalization, ETL pipeline, EDA analysis and TFIDF tokenization based matching. }
%---------------------------------------------------------
\end{cventries}
